%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% One Page Two Column Resume
% LaTeX Template
% Version 1.3 (14/8/2015)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{resume}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COVER LETTER
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{\fill}  % vertically center
\hspace{-6mm} % hack to remove tab vertical space was causing
Nickolas Balboni  \\
226 Parker Hill Ave.  \\
Boston, MA 02120  \\
\\
Josh Hern\'{a}ndez, Technical Recruiter \\
3200 Ash St.  \\
Palo Alto, CA 94306  \\
\\~\\
October 25, 2016  \\
\\
Dear Josh Hern\'{a}ndez,  \\
\\

% Paragraph 1:
% - why are you writing this letter
% - your objective contacting this person
% - title of position + company name
% - sources for info on company and position
% - how position within company would enhance your career path
I am writing this letter in the hopes of pursuing a position at Robinhood.  By contacting you I hope to set up an interview at the company.  The position I wish to pursue is the Web Engineer job opening at Robinhood.  I have been trading with the Robinhood app since January of 2015, but I was closely following the company before they even had released their product.  The company's mission to make financial markets more accessible continues to excite me, and the app continues to impress me.  I discovered the job opening through the company's website.  I feel that the opportunity to work as a web engineer for Robinhood would directly align with my career goals.  The position and the company would allow me to pursue my two greatest interests:  software development, and financial investment.  \\
\\

% Paragraph 2:
% - current education status + how it's prepared you for this job
% - practical experience obtained outside classroom
% - skills gained from past work experience
% - summarize personal attributes + how'd they help in the workplace
I am currently entering my final year as a computer engineering major at Northeastern University.  Northeastern has done a tremendous job preparing me for the workplace, and through my computer engineering coursework I have studied the inner workings of programming languages, software development algorithms, computer networks, and network security.  Throughout my time in school, I have worked hard to supplement my coursework with independent projects, and freelance jobs writing software.  These projects allow me to explore different languages and ecosystems that my coursework does not touch on.  My exploration has been continued by the job opportunities I have had during summer breaks and on my Co-ops.  My first job experience, at B2W Software, introduced me to web development, in the context of a hybrid mobile app.  Then, at Charles River Development, I was able to get a glimpse at how software shapes the infrastructure of financial markets, working on an application for trade matching, and settlement instruction workflows.  At my most recent job, with Tablelist, I was able to work on a small startup team doing iOS, Node, and Angular development.  In addition to my technical skills, I have a strong work ethic and a drive for perfection that results in beautiful, maintainable products.  \\
\\

% Paragraph 3:
% - restate interest in position
% - provide phone number
% - thank employer for their time
The Web Engineer position at Robinhood is a perfect fit for me.  My interests, skills, and drive will allow me to thrive in role this opportunity provides.  I can be reached by email, at balboni.n@husky.neu.edu, or by phone, at (603) 819-8895.  I hope to be able to meet you in the future.  Thank you so much for your time.  \\
\\[1.5cm]
Sincerely,  \\
\\[1cm]
Nickolas Balboni \\
\\[2cm]
\vspace*{\fill}  % vertically center
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Nickolas}{Balboni}{\href{mailto:balboni.n@husky.neu.edu}{balboni.n@husky.neu.edu} | (603) 819-8895
}{ Website: \\ GitHub: \\ LinkedIn: \\ StackOverflow: \\ }{
\urlstyle{same}\url{http://nickbalboni.com} \\
\urlstyle{same}\url{http://github.com/SwankSwashbucklers} \\
\urlstyle{same}\url{http://linkedin.com/in/nickbalboni} \\
\urlstyle{same}\url{http://stackoverflow.com/users/2615252} \\ }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Northeastern University}
\descript{BS in Computer Engineering}
\location{Expected January 2018 | Boston, MA}
\location{ GPA: 3.19 / 4.0}
\location{ Major GPA: 3.46 / 4.0}
\sectionsep

\subsection{Phillips Exeter Academy}
\location{Grad. May 2013 |  Exeter, NH}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\custsubhead{Network Security}
\hspace{8pt} SSL/TLS, IPsec, OAuth, WPA \\
\hspace{8pt} RSA, Diffie-Hellman \\
\hspace{8pt} DOS, Viruses, Worms \\
\vspace{4pt}
\custsubhead{Fundamentals of Networks}
\hspace{8pt} Internet Protocols \\
\hspace{8pt} Computer Networks; Python \\
\vspace{4pt}
\custsubhead{Programming Languages}
\hspace{8pt} Development of languages \\
\hspace{8pt} Method dispatch; concurrency \\
\vspace{4pt}
\custsubhead{Fundamentals of Eng. Algorithms}
\hspace{8pt} C++; Sorting, Tree and Graph \\
\hspace{8pt} Algorithms; Algorithm Analysis\\
\vspace{4pt}
\custsubhead{Principles of Microeconomics}
\hspace{8pt} Supply, Demand, Market Price \\
\hspace{8pt} Monopoly; Competition \\
\vspace{4pt}
\custsubhead{Embedded Des. Enabling Robotics}
\hspace{8pt} Unix; C; Wireless Networking \\
\vspace{4pt}
\custsubhead{Engineering Problem Solving}
\hspace{8pt} C++; MatLAB \\
\vspace{4pt}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\custsubhead{Proficient: }
\hspace{8pt} Python \textbullet{} JavaScript/AngularJS  \\
\hspace{8pt} Objective-C/iOS \textbullet{} CSS/Sass \\
\custsubhead{Comfortable: }
\hspace{8pt} Java \textbullet{} C++ \textbullet{} C \textbullet{} MongoDB \\
\hspace{8pt} Bottle/Flask \textbullet{} Bash \\
\custsubhead{Familiar: }
\hspace{8pt} C\# \textbullet{} Android \textbullet{} MySQL
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ABOUT ME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{About Me}
\hspace{8pt}
\begin{tightemize} \item Enjoy playing guitar and \\ piano; compose pieces of \\ music in my free time. \item Love to code! \end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Tablelist}
\descript{| Software Development Co-op }
\location{January 2016 – Present | Boston, MA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize} \item Work as a full-stack developer on web, server, and iOS products. \item Develop in AngularJS, Node.js, Swift, and Mongoose. \item Built the curated lists module for the company's admin portal. \item Built, and took ownership of a repository of Jinja templates and Python scripts for managing email distribution for Tablelist projects.  \item Refactored server notification code to work with the new templates and service. \item Implemented tiered-ticketing on NightPro, the company's venue management app. \end{tightemize}
\sectionsep

\runsubsection{Charles River Development}
\descript{| Software Engineering Co-op }
\location{January – July 2015 | Burlington, MA}
\begin{tightemize} \item Worked on the Post-Trade team writing bug fixes and unit-tests in Java. \item Created various Python scripts to assist with QA work. \item Took ownership of the team's automation testing project, repairing and maintaining it. \item Advanced abilities working in an agile setting (specifically scrum).  \item Obtained insight into the workings of financial markets. \end{tightemize}
\sectionsep

\runsubsection{B2W Software}
\descript{| Software Engineering Intern }
\location{Summer of 2013 \& 2014 | Portsmouth, NH}
\begin{tightemize} \item Worked on both the Mobile and Maintain teams filling various responsibilities. \item Created the first iteration for the equipment section of the maintenance module, which was pushed into production in the 2014 release. \item Gained experience with release testing, on both iOS and Android tablets. \item Worked on the cross-platform tablet application, coding in Javascript with the Kendo UI framework, and working with PhoneGap. \item Designed and developed a continuous integration system for ad hoc deployment of the B2W Mobile application. \end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Apps With Style, LLC}
\descript{| Co-Founder \& Software Developer }
\location{January 2014 – Present | Exeter, NH}
\begin{tightemize} \item Create mobile applications for clients, and applications for distribution under the company developer account. \item Develop mobile applications using both native iOS development (i.e. Swift, Objective-C, Core Data, Interface Builder, and Size Classes), and cross-platform development (i.e. Phonegap, Javascript, AngularJS, CSS, and HTML) \item Completed and released an iOS password and account manager called passKey, which is out on the Apple app store today.\item Acquire experience running and maintaining a business. \item Created a company website: \urlstyle{same}\url{http://appswithstyle.net}, for showcasing applications and company information. \end{tightemize}
\sectionsep

\runsubsection{Websitr}
\descript{| Github:// \href{https://github.com/SwankSwashbucklers/websitr}{ \bf websitr}}
\fontspec[Path = fonts/raleway/]{Raleway-Medium}\fontsize{10pt}{12pt}\selectfont {} \normalfont
\begin{tightemize} \item A python script for creating a website/webapp project. \item Complete with a python build-tool for favicon, css, and route generation. \end{tightemize}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
